03_wrangle

### 2020-08-28 analysis/03_datawrangling.Rmd
new DEGs

allvsd <- vsd_pathfiles %>%
  setNames(nm = .) %>% 
  map_df(~read_csv(.x), .id = "file_name")  %>% 
  dplyr::rename("gene" = "X1") %>% 
  #pivot_longer(cols = L.G118_female_gonad_control:y98.o50.x_male_pituitary_inc.d3, 
               #names_to = "samples", values_to = "counts") 
  pivot_longer(cols = L.Blu13_male_hypothalamus_control.NYNO:y98.o50.x_male_hypothalamus_inc.d3, 
               names_to = "samples", values_to = "counts") 
allvsd %>% select(-file_name) %>% head()

@@

manipDEGs <- rbind(removalDEGs, hatchDEGs) %>%
  rbind(., prolongDEGs) %>%
  arrange(desc(n))
head(manipDEGs)
```

@@

```{r write}
write.csv(allDEG, "../results/03_allDEG.csv", row.names = F)
write.csv(candidatevsd, "../results/03_candidatevsd.csv")
write.csv(wideDEGsSequential, "../results/table1.csv", row.names = F)
write.csv(manipDEGs, "../results/manipDEGs.csv")
```

@@

```{r}

@@

```{r}

@@

```{r}

>>>>

allvsd <- vsd_pathfiles %>%
  setNames(nm = .) %>% 
  map_df(~read_csv(.x), .id = "file_name")  %>% 
  dplyr::rename("gene" = "X1") %>% 
  pivot_longer(cols = L.G118_female_gonad_control:y98.o50.x_male_pituitary_inc.d3, 
               names_to = "samples", values_to = "counts") 
allvsd %>% select(-file_name) %>% head()

@@

manipDEGs <- rbind(removalDEGs, earlyDEGs) %>%
  rbind(., prolongDEGs) %>%
  rbind(., extendDEGs) %>%
  arrange(desc(n))
head(manipDEGs)
```

@@

```{r write}
write.csv(allDEG, "../results/03_allDEG.csv", row.names = F)
write.csv(candidatevsd, "../results/03_candidatevsd.csv")
#write.csv(wideDEGsSequential, "../results/table1.csv", row.names = F)
write.csv(manipDEGs, "../results/manipDEGs.csv")
write.csv(wideDEGscandidates, "../results/03_wideDEGscandidates.csv", row.names = F)

@@

```{r venn-rm}

@@

```{r venn-chicks}

@@

```{r venn-eggs}
